Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of neutron star - black hole binary observations

### 2016-10-17 Paper/paper.tex
improved fig 3,4
explanation of why we use injected values for median TT

for $\arr_{\mchirp}=10\%, 25\%, 50\%\cdots$, with interleaving color levels
separated by $5\%$.

@@

measurement errors for BH spins, with other attributes identical to 
Fig.~\ref{fig:TN_chirpMassBias_vs_Lambda_SNR}, and~\ref{fig:TN_EtaBias_vs_Lambda_SNR}.

@@

% %% FIXME FIXME
% \textbf{Illustrative posterior probability distributions for NSBH parameters,}\par
% \textbf{for signals at different SNR values; $\rho = 20$ (left) and $50$ (right).}\par\medskip
% \includegraphics[width=1.05\columnwidth,trim=2cm 0 0 0]{plots/AllParamsMcEtPDF1D2D_q4_mc2_25_chi0_50_snr20}%\\
% \includegraphics[width=1.05\columnwidth,trim=2cm 0 0 0]{plots/AllParamsMcEtPDF1D2D_q4_mc2_25_chi0_50_snr50}%\\
% % \includegraphics[width=0.5\columnwidth]{plots/McEta2D_q4_mc2_25_chi0_50_snr30}
% % \includegraphics[width=0.5\columnwidth]{plots/EtaChiBH2D_q4_mc2_25_chi0_50_snr30}
% % \includegraphics[width=0.5\columnwidth]{plots/McChiBH2D_q4_mc2_25_chi0_50_snr30}\\
% % \includegraphics[width=0.5\columnwidth]{plots/LambdaMc2D_q4_mc2_25_chi0_50_snr30}
% % \includegraphics[width=0.5\columnwidth]{plots/LambdaEta2D_q4_mc2_25_chi0_50_snr30}
% % \includegraphics[width=0.5\columnwidth]{plots/LambdaChiBH2D_q4_mc2_25_chi0_50_snr30}\\
% % \includegraphics[width=0.47\columnwidth]{plots/LambdaMc2D_q4_mc2_25_chi0_50_snr50}
% % \includegraphics[width=0.47\columnwidth]{plots/LambdaEta2D_q4_mc2_25_chi0_50_snr50}
% % \includegraphics[width=0.47\columnwidth]{plots/LambdaChiBH2D_q4_mc2_25_chi0_50_snr50}
% We illustrate here two-dimensional joint probability distributions, as
% recovered for the intrinsic parameters of a binary with
% $q = \mbh/\mns = 5.4M_\odot/1.35M_\odot = 4$, $\chibh=+0.5$,
% $\lambdans=2000$, and $\rho=30$ (same as in
% Fig.~\ref{fig:SingleSystemLambdaPDFvsSNR}).
% The top row shows the same for combinations of 
% non-tidal parameters, i.e. binary masses and spins, while the middle row 
% shows combinations of $\lambdans$ with non-tidal parameters. The bottom row
% is similar to the middle, with the only difference being that the SNR has been
% turned up to $\rho=50$.
% \label{fig:SingleSystemLambda2DPDFs}
% \textbf{Statistical uncertainty in $\lambdans$ measurement}\par\medskip
% \includegraphics[trim={2cm 0 0 0},width=2.2\columnwidth]{plots/TTLambdaRawCIWidths90_0_Lambda_SNR}
% % \includegraphics[trim={3cm 0 0 0},width=2.\columnwidth]{plots/TTLambdaCIWidths90_0_Lambda_SNR.pdf}
% \caption{Here we show the statistical uncertainty in the measurement of
% $\lambdans$, as a percentage of the injected/true value. In each panel, the
% same is shown as a function of the BH mass and spin, keeping $\lambdans$ and
% injection's SNR $\rho$ fixed (noted in the panel). Rows contain panels
% with the same value of $\lambdans$, with $\rho$ increasing from left to right.
% Each column contains panels with the same value of $\rho$, with $\lambdans$ 
% increasing from top to bottom.
% Contours demarcate regions where we can constrain the
% $\lambdans$ parameter well (within a factor of two of the injected value).
% We note that, as expected, the measurement accuracy for $\lambdans$ improves with (i) increasing
% SNR, (ii) decreasing BH mass, (iii) increasing BH spin, and 
% (iv) increasing $\lambdans$, i.e. the tidal deformability of the neutron star.
% \label{fig:TT_LambdaCIWidths90_0_Lambda_SNR}

@@

As an illustration, in Fig.~\ref{fig:SingleSystemEtaPDFvsSNR} we show the
recovered probability distributions for binary mass ratio $\eta$ for
three NSBH injections, with $\rho=20$ (left), $30$ (middle), and $\rho=50$
(right), and other parameters held fixed ($\mns=1.35M_\odot$, $\chins=0$,
$\mbh=5.4M_\odot$, $\chibh=+0.5$ and $\lambdans=2000$). In each panel, both
the {\it true} and the median values of $\eta$ are marked.
The effect of ignoring tidal corrections in templates manifests as a systematic
shift of the median $\eta$ value away from its true value. We measure
the associated {\it systematic} bias/error by the differences between the
true and median $\eta$ values. Darker
shading of the probability distributions marks the $90\%$ credible interval,
whose width $(\Delta\eta)^{90.0\%}$ is a direct measure of the
{\it statistical} measurement uncertainty/error\footnote{We generalize the
notation $(\Delta X)^{90.0\%}$ to mean the $90\%$ credible interval width
for any measured source parameter $X$.}.
% 
We see clearly that even when the signal is moderately loud, with $\rho=20$,
statistical errors dominate over systematics for $\eta$. As we turn up the SNR
further, we find that the two error sources become comparable at $\rho\sim 30$,
and systematic errors dominate finally when $\rho\simeq 50$.

>>>>

for $\arr_{\mchirp}=10\%, 25\%, 50\%\cdots$, with interleaving filled color
levels separated by $5\%$.

@@

measurement errors for BH spins $\arr_{\chibh}$. Information is arranged identically
to Fig.~\ref{fig:TN_chirpMassBias_vs_Lambda_SNR}, 
and~\ref{fig:TN_EtaBias_vs_Lambda_SNR}, with the level spacing of filled contours
increased to $15\%$.

@@

@@

The effect of ignoring
tidal corrections in templates will manifest as a systematic shift
of recovered median parameter values away from what they would be if we had used
tidal templates with identical priors. 
In zero noise, we expect the probability distributions recovered using tidal
templates to be multi-dimensional Gaussians with the maximum likelihood
parameter values approaching their true values. If the priors are not
restrictive, we expect the recovered median to also converge to the true value.
However,
the LEA model imposes significantly more restrictive priors (both mass-ratio
and spin) than SEOBNRv2~\cite{Taracchini:2013rva,Lackey:2013axa}, which shifts
the median value of parameters recovered using {\it our} tidal templates away
from their true value. If we use LEA+ priors for our non-tidal templates, it
would add a caveat to our original question 'can we estimate non-tidal NSBH
parameters with equivalent BBH templates'. Instead, we approximate the median
tidally recovered parameters by their true injected values, as one would expect
to recover with an ideal model for tidally disruptive NSBH mergers. With this
caveat, we estimate {\it systematic} measurement bias/errors as the
differences between median and {\it injected} parameter values. 
% 
As an illustration, in Fig.~\ref{fig:SingleSystemEtaPDFvsSNR} we show the
recovered probability distributions for binary mass ratio $\eta$ for
three NSBH injections, with $\rho=20$ (left), $30$ (middle), and $\rho=50$
(right), and other parameters held fixed ($\mns=1.35M_\odot$, $\chins=0$,
$\mbh=5.4M_\odot$, $\chibh=+0.5$ and $\lambdans=2000$). In each panel, both
the {\it true} and median values of $\eta$ are marked, and we use
the shift between the red and green vertical lines as our estimate of systematic
measurement errors. Darker shading in all panels marks $90\%$ credible intervals,
whose width $(\Delta\eta)^{90.0\%}$ we use as a direct measure of our
{\it statistical} measurement uncertainty/error\footnote{We generalize the
notation $(\Delta X)^{90.0\%}$ to mean the $90\%$ credible interval width
for any measured source parameter $X$.}.
% 
For the illustrated binary,
we see clearly that even when the signal is moderately loud, with $\rho=20$,
statistical errors dominate over systematics for $\eta$. As we turn up the SNR
further, the two error sources become comparable at $\rho\sim 30$,
and systematic errors dominate finally when $\rho\simeq 50$.
